Thread Pool in GeckoDB/BOLSTER - Implementing a Thread Pool for a High Performance Database System \\

### 2018-07-06 Presentations/Paper/paper_thread_pool.tex
Fix typos and or grammar

For testing purposes we used primarly Linux setups, for one Ubuntu 17.04
(linux 4.13) in an virtual machine environment, second Archlinux (linux
4.17.2-1) running native, both updated on stable branch. Tests have also been
conducted on Windows 10 and macOs HighSierra machines.

@@

\subsection{Validity of Results}
Before presenting our evaluation results, we give some preliminaries about the validity of our results. At first, all measurements are executed on all machines we listed in our experimental configuration, but in this work we present only the results measured on Archlinux with kernel 4.17.2-1 and 24 GB DDR4-SODIMM. We decided to use this system, since it is running on a high kernel version and not in a virtual environment. Additionally, we use gnuplot to generate diagrams from our results, consequently using a windows machine is not optimal.

>>>>

For testing purposes we used primarly Linux setups, for one Ubuntu 17.04
(linux 4.13) in an virtual machine environment, second Archlinux (linux
4.17.3-1) running native, both updated on stable branch. Tests have also been
conducted on Windows 10 and macOs HighSierra machines.

@@

\subsection{Validity of Results} 
Before presenting our evaluation results, we
give some preliminaries about the validity of our results. At first, all
measurements are executed on all machines we listed in our experimental
configuration, but in this work we present only the results measured on
Archlinux with kernel 4.17.3-1 and 24 GB DDR4-SODIMM. We decided to use this
system, since it is running a current kernel version and not in a virtual
environment. Additionally, we use gnuplot to generate diagrams from our results,
consequently using a windows machine is not optimal.
